Draft Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-06-12 draftfinalreport_v4.Rnw
fixup table centering

\vspace{5mm} %5mm vertical space
\begin{table}
<<include=FALSE,echo=FALSE,results=tex>>=
print(resan,floating = FALSE)
@
\caption{Significance of different predictor variables for measles risk factors from 2007-2014, estimated using \autoref{eq:reg} and a quasipoisson error structure. Pr($>$F) is p-value, the statistical significance of the result}
\label{table:anova}
\end{table}

\vspace{5mm} %5mm vertical space
\begin{table}
<<include=FALSE,echo=FALSE,results=tex>>=
  print(xtb,floating = FALSE)
@
\caption{Summary of the regression model results using \autoref{eq:reg} and a quasipoisson error structure, for measles risk factors for cases from 2007-12 June 2014. Estimate: negative values indicate rates are lower for this category compared to the base category, which does not appear (e.g. Age 5--17 has a lower measles rate per capita compared to the 0--1 age class that is not shown), and positive values indicate the rates are greater than the baseline rate; Std. error is the standard error, a measure of uncertainty in the estimates; and Pr(>|t|) is the p-value, the statistical significance of the result.}
\label{table:regression_riskfactors}
\end{table}

>>>>

\vspace{5mm} %5mm vertical space
\begin{table}
\begin{center}
<<include=FALSE,echo=FALSE,results=tex>>=
print(resan,floating = FALSE)
@
\caption{Significance of different predictor variables for measles risk factors from 2007-2014, estimated using \autoref{eq:reg} and a quasipoisson error structure. Pr($>$F) is p-value, the statistical significance of the result}
\label{table:anova}
\end{center}
\end{table}

\vspace{5mm} %5mm vertical space
\begin{table}
\begin{center}
<<include=FALSE,echo=FALSE,results=tex>>=
  print(xtb,floating = FALSE)
@
\caption{Summary of the regression model results using \autoref{eq:reg} and a quasipoisson error structure, for measles risk factors for cases from 2007-12 June 2014. Estimate: negative values indicate rates are lower for this category compared to the base category, which does not appear (e.g. Age 5--17 has a lower measles rate per capita compared to the 0--1 age class that is not shown), and positive values indicate the rates are greater than the baseline rate; Std. error is the standard error, a measure of uncertainty in the estimates; and Pr(>|t|) is the p-value, the statistical significance of the result.}
\label{table:regression_riskfactors}
\end{center}
\end{table}
